---
title: "Pipeline Summary"
format: 
  html: 
    page-layout: full
    embed-resources: true
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| echo: false

tar_load(vct_raw)
tar_load(vct_basic)
tar_load(lst_out.cut)
tar_load(vct_cal)
tar_load(lst_out.raw)
tar_load(lst_out.oak.pre)
tar_load(vct_ox_step)
tar_load(vct_ox_wlms)
tar_load(vct_ox_acti)
tar_load(fpa_merged)

len_raw <- length(vct_raw)
df_out <- summarize_major_steps(
  vct_raw,
  vct_basic,
  vct_cal,
  lst_out.raw,
  lst_out.oak.pre,
  lst_out.cut,
  vct_ox_step,
  vct_ox_wlms,
  vct_ox_acti
)
lgl_all <- 
  df_out |> 
  rowwise() |> 
  mutate(
    all = all(c_across(
      GGIR:actinet
    ))
  ) |> 
  pull(all)
lst_summary <- summarize_metrics_main(fpa_merged)

```

# Input

Out of `r len_raw` raw files, `r sum(lgl_all)` successfully went through the pipeline.

# By Major Steps

Below is a table listing if each major step was successful for a file (TRUE) or unsuccessful (FALSE)

```{r}
#| label: tbl-major
#| echo: false
tbl_out

```

# Totals by Configuration File

If all values are highlighted green, then the WAVES code is running successfully on your computer. If a column or row is highlighted in red, please share this .html file with the WAVES data team for follow up.

## MVPA (minutes)

```{r}
#| label: tbl-mvpa_total 
#| echo: false 
lst_summary$total_mvpa

```

## Sedentary (minutes)

```{r}
#| label: tbl-mvpa_total 
#| echo: false 
lst_summary$total_sed

```

## Steps

```{r}
#| label: tbl-mvpa_total 
#| echo: false 
lst_summary$total_step

```

# tar_meta

```{r}
#| label: tar_meta
#| echo: false

tar_meta()$warnings |> 
  mutate(
    warnings = gsub(
      x = warnings,
      pattern = "\\w{0,1}package '.*' was built under R version 4.5.2.",
      replacement = ""
    )
  ) |> 
  kable()

```
