---
title: "Configuration Pipeline Summary"
format: 
  html: 
    toc: true
    page-layout: full
  typst: 
    toc: true
    mainfont: arial
    papersize: presentation-16-9
    margin:
      x: 1cm
      y: 1cm
    pdf-standard: ua-1
editor: source
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| echo: false

library(targets)
source("packages.R") |>
  suppressMessages() |>
  suppressWarnings()
list.files(
  path       = "R",
  pattern    = "\\.R$",
  full.names = TRUE
) |>
  grep(x       = _,
       pattern = "^R\\/_",
       value   = TRUE,
       invert  = TRUE) |>
  sapply(FUN = source) |>
  invisible()
tar_load(vct_raw)
tar_load(vct_basic)
tar_load(vct_nw.sleep)
tar_load(vct_out.cut)
tar_load(vct_cal)
tar_load(vct_out.raw)
tar_load(vct_out.oak.pre)
tar_load(vct_ox_step)
tar_load(vct_ox_wlms)
tar_load(vct_ox_acti)
tar_load(df_pipe)
lst_info <- jsonlite::fromJSON(Sys.getenv("QUARTO_EXECUTE_INFO"))
target_format <- lst_info$format$identifier$`target-format`

len_raw <- length(vct_raw)
df_out <- summarize_major_steps(
  vct_raw,
  vct_basic,
  vct_nw.sleep,
  vct_cal,
  vct_out.raw,
  vct_out.oak.pre,
  vct_out.cut,
  vct_ox_step,
  vct_ox_wlms,
  vct_ox_acti
)
df_test_out <- tibble(
  file = c(
    "WAVES_10002_RAW.csv.gz",
    "WAVES_10003_RAW.csv.gz",
    "WAVES_10004_RAW.gt3x",
    "WAVES_10005_RAW.cwa",
    "WAVES_10006_RAW.csv.gz"
  ),
  GGIR = c(
    FALSE, FALSE, TRUE, TRUE, TRUE
  ),
  nw.sleep = c(
    FALSE, FALSE, TRUE, TRUE, TRUE
  ),
  calibration = c(
    FALSE, FALSE, TRUE, TRUE, TRUE
  ),
  `raw methods` = c(
    FALSE, FALSE, TRUE, TRUE, TRUE
  ),
  oak.pre = c(
    FALSE, FALSE, TRUE, TRUE, TRUE
  ),
  cutpoints = c(
    FALSE, FALSE, TRUE, TRUE, TRUE
  ),
  stepcount = c(
    FALSE, FALSE, TRUE, TRUE, FALSE
  ),
  walmsley = c(
    FALSE, FALSE, TRUE, TRUE, FALSE
  ),
  actinet = c(
    FALSE, FALSE, TRUE, TRUE, FALSE
  )
)
# common_files <- intersect(df_out$file, df_test_out$file)
# common_cols <- intersect(names(df_out), names(df_test_out))
# common_cols <- c("file", setdiff(common_cols, "file"))
# 
# df_out <-
#   df_out |>
#   filter(.data$file %in% common_files) |>
#   select(all_of(common_cols)) |>
#   arrange(.data$file)
# cli::cli_abort("Made it this far.")
# 
# df_test_out <-
#   df_test_out |>
#   filter(.data$file %in% common_files) |>
#   select(all_of(common_cols)) |>
#   arrange(.data$file)

df_equal <- 
  (df_out[, -1] == df_test_out[, -1]) |>
  as.data.frame() |>
  mutate(file = df_out$file, .before = 1) |>
  pivot_longer(cols = !file,
               names_to = "step",
               values_to = "equal") |>
  mutate(
    rowid = rleid(file),
    clr = ifelse(
      equal,
      yes = "#D9F1D5",
      no  = "#ea9999"
    )
  )
tbl_out <- gt(df_out)

for (i in seq_len(nrow(df_equal))) {
  tbl_out <-
    tbl_out |>
    tab_style(
      style = cell_fill(color = df_equal$clr[i]),
      locations = cells_body(columns = df_equal$step[i],
                             rows = df_equal$rowid[i])
    )
}

lgl_all <- 
  df_out |> 
  rowwise() |> 
  mutate(
    all = all(c_across(
      GGIR:actinet
    ))
  ) |> 
  pull(all)
lst_summary <- summarize_metrics_config(df_pipe)
lst_methods <- lapply(
  lst_summary,
  \(x) {
    extract_body(x) |> 
      names() |> 
      stri_replace(regex = "id|method|Yours_|WAVES_",
                   replacement = "") |>
      unique() |> 
      stri_remove_empty()
  }
)

```

# Input

Out of `r len_raw` configuration test files, `r sum(lgl_all)` successfully went through the entire pipeline.

# By Major Steps

Below is a table listing if each major step was successful for a file (TRUE) or unsuccessful (FALSE)

```{r}
#| label: major
#| echo: false
tbl_out

```

# Summary Metrics

## Totals by Configuration File

If all values are highlighted green, then the WAVES code is running successfully on your computer. If a column or row is highlighted in red, please share this .html file with the WAVES data team for follow up.

### MVPA (minutes)

```{r}
#| label: mvpa_total
#| echo: false
#| results: asis

if (target_format == "html") {
  lst_summary$total_mvpa
} else {
  # can't get the function to work so just type it out.
  # print_total_gt(
  #   lst_summary = lst_summary,
  #   lst_methods = lst_methods,
  #   le_tbl      = "total_mvpa",
  #   size        = 4
  # )
  le_tbl <- "total_mvpa"
  size   <- 5
  lst_split <- split_in_seq(lst_methods[[le_tbl]], size = size)
  for (i in seq_along(lst_split)) {
    vct_hide <-
      lst_methods[[le_tbl]][!lst_methods[[le_tbl]] %in% lst_split[[i]]]
    le_gt <-
      lst_summary[[le_tbl]] |>
      cols_hide(
        matches(paste0(vct_hide, collapse = "|"))
      ) |>
      cols_width(
        matches("id") ~ pct(20),
        everything()  ~ pct(8)
      )
    cat(
      knitr::knit_child(
        text = c(
          "```{r}",
          "#| echo: false",
          "le_gt",
          "```"
        ),
        quiet = TRUE
      ),
      sep = "\n"
    )
  }
}

```

### Sedentary (minutes)

```{r}
#| label: sed_total
#| echo: false
#| results: asis

if (target_format == "html") {
  lst_summary$total_sed
} else {
  le_tbl <- "total_sed"
  size   <- 5
  lst_split <- split_in_seq(lst_methods[[le_tbl]], size = size)
  for (i in seq_along(lst_split)) {
    vct_hide <-
      lst_methods[[le_tbl]][!lst_methods[[le_tbl]] %in% lst_split[[i]]]
    le_gt <-
      lst_summary[[le_tbl]] |>
      cols_hide(
        matches(paste0(vct_hide, collapse = "|"))
      ) |>
      cols_width(
        matches("id") ~ pct(20),
        everything()  ~ pct(8)
      )
    cat(
      knitr::knit_child(
        text = c(
          "```{r}",
          "#| echo: false",
          "le_gt",
          "```"
        ),
        quiet = TRUE
      ),
      sep = "\n"
    )
  }
}

```

### Steps

```{r}
#| label: step_total
#| echo: false
#| results: asis

if (target_format == "html") {
  lst_summary$total_step
} else {
  le_tbl <- "total_step"
  size   <- 5
  lst_split <- split_in_seq(lst_methods[[le_tbl]], size = size)
  for (i in seq_along(lst_split)) {
    vct_hide <-
      lst_methods[[le_tbl]][!lst_methods[[le_tbl]] %in% lst_split[[i]]]
    le_gt <-
      lst_summary[[le_tbl]] |>
      cols_hide(
        matches(paste0(vct_hide, collapse = "|"))
      ) |>
      cols_width(
        matches("id") ~ pct(20),
        everything()  ~ pct(8)
      )
    cat(
      knitr::knit_child(
        text = c(
          "```{r}",
          "#| echo: false",
          "le_gt",
          "```"
        ),
        quiet = TRUE
      ),
      sep = "\n"
    )
  }
}

```

## Agreement Matrices

Bottom left of matrices represent summary agreement between methods, as calculated from the pipeline on your computer. Top right of matrices represent summary agreement between methods, as calculated by WAVES team. If all values on the bottom left side are highlighted green, then the WAVES code is running successfully on your computer. If a column or row is highlighted in red, please share this .html file with the WAVES data team for follow up.

### MVPA (Percent Agreement)

```{r}
#| label: mvpa_agree
#| echo: false
#| results: asis

if (target_format == "html") {
  lst_summary$agree_mvpa
} else {
  # can't get the function to work so just type it out.
  # print_agree_gt(
  #   lst_summary = lst_summary,
  #   lst_methods = lst_methods,
  #   le_tbl      = "agree_mvpa",
  #   size        = 4
  # )
  le_tbl <- "agree_mvpa"
  size   <- 5
  lst_split <- split_in_seq(lst_methods[[le_tbl]], size = size)
  for (i in seq_along(lst_split)) {
    ind_methods <- which(lst_methods[[le_tbl]] %in% lst_split[[i]])
    le_df <- 
      lst_summary[[le_tbl]][["_data"]] |>
      select(c(1, ind_methods + 1)) |> 
      slice(ind_methods)
    le_styles <- 
      lst_summary[[le_tbl]][["_styles"]] |> 
      dplyr::filter(colname %in% names(le_df)[-1],
                    rownum %in% ind_methods) |> 
      mutate(
        colname = recode_values(
          colname,
          from = names(le_df)[-1],
          to   = le_df$method
        ),
        rownum = rownum - (5 * (i - 1))
      )
    names(le_df) <- c(
      "Method",
      le_df$method
    )
    le_gt <-
      le_df |> 
      gt() |> 
      cols_width(
        matches("Method") ~ pct(20),
        everything()      ~ pct(16)
      )
    for (ii in seq_len(nrow(le_styles))) {
      le_gt <-
        le_gt |>
        tab_style(
          style = cell_fill(color = le_styles$styles[[ii]]$cell_fill$color),
          locations = cells_body(columns = le_styles$colname[ii],
                                 rows = le_styles$rownum[ii])
        )
    }
    cat(
      knitr::knit_child(
        text = c(
          "```{r}",
          "#| echo: false",
          "le_gt",
          "```"
        ),
        quiet = TRUE
      ),
      sep = "\n"
    )
  }
}

```

### Sedentary (Percent Agreement)

```{r}
#| label: sed_agree
#| echo: false
#| results: asis

if (target_format == "html") {
  lst_summary$agree_sed
} else {
  le_tbl <- "agree_sed"
  size   <- 5
  lst_split <- split_in_seq(lst_methods[[le_tbl]], size = size)
  for (i in seq_along(lst_split)) {
    ind_methods <- which(lst_methods[[le_tbl]] %in% lst_split[[i]])
    le_df <- 
      lst_summary[[le_tbl]][["_data"]] |>
      select(c(1, ind_methods + 1)) |> 
      slice(ind_methods)
    le_styles <- 
      lst_summary[[le_tbl]][["_styles"]] |> 
      dplyr::filter(colname %in% names(le_df)[-1],
                    rownum %in% ind_methods) |> 
      mutate(
        colname = recode_values(
          colname,
          from = names(le_df)[-1],
          to   = le_df$method
        ),
        rownum = rownum - (5 * (i - 1))
      )
    names(le_df) <- c(
      "Method",
      le_df$method
    )
    le_gt <-
      le_df |> 
      gt() |> 
      cols_width(
        matches("Method") ~ pct(20),
        everything()      ~ pct(16)
      )
    for (ii in seq_len(nrow(le_styles))) {
      le_gt <-
        le_gt |>
        tab_style(
          style = cell_fill(color = le_styles$styles[[ii]]$cell_fill$color),
          locations = cells_body(columns = le_styles$colname[ii],
                                 rows = le_styles$rownum[ii])
        )
    }
    cat(
      knitr::knit_child(
        text = c(
          "```{r}",
          "#| echo: false",
          "le_gt",
          "```"
        ),
        quiet = TRUE
      ),
      sep = "\n"
    )
  }
}

```

### Steps (Correlation)

```{r}
#| label: step_agree
#| echo: false
#| results: asis

if (target_format == "html") {
  lst_summary$cor_step
} else {
  le_tbl <- "cor_step"
  size   <- 5
  lst_split <- split_in_seq(lst_methods[[le_tbl]], size = size)
  for (i in seq_along(lst_split)) {
    ind_methods <- which(lst_methods[[le_tbl]] %in% lst_split[[i]])
    le_df <- 
      lst_summary[[le_tbl]][["_data"]] |>
      select(c(1, ind_methods + 1)) |> 
      slice(ind_methods)
    le_styles <- 
      lst_summary[[le_tbl]][["_styles"]] |> 
      dplyr::filter(colname %in% names(le_df)[-1],
                    rownum %in% ind_methods) |> 
      mutate(
        colname = recode_values(
          colname,
          from = names(le_df)[-1],
          to   = le_df$method
        ),
        rownum = rownum - (5 * (i - 1))
      )
    names(le_df) <- c(
      "Method",
      le_df$method
    )
    le_gt <-
      le_df |> 
      gt() |> 
      cols_width(
        matches("Method") ~ pct(20),
        everything()      ~ pct(16)
      )
    for (ii in seq_len(nrow(le_styles))) {
      le_gt <-
        le_gt |>
        tab_style(
          style = cell_fill(color = le_styles$styles[[ii]]$cell_fill$color),
          locations = cells_body(columns = le_styles$colname[ii],
                                 rows = le_styles$rownum[ii])
        )
    }
    cat(
      knitr::knit_child(
        text = c(
          "```{r}",
          "#| echo: false",
          "le_gt",
          "```"
        ),
        quiet = TRUE
      ),
      sep = "\n"
    )
  }
}

```
