---
title: "Pipeline Summary"
format: 
  html:  
    toc: true
    page-layout: full
editor: source
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| echo: false

library(targets)
source("packages.R") |>
  suppressMessages() |>
  suppressWarnings()
tar_load(lst_yaml)
tar_load(vct_out.ref)
tar_load(vct_raw)
tar_load(vct_basic)
tar_load(vct_nw.sleep)
tar_load(vct_out.cut)
tar_load(vct_cal)
tar_load(vct_out.raw)
tar_load(vct_out.oak.pre)
tar_load(vct_ox_step)
tar_load(vct_ox_wlms)
tar_load(vct_ox_acti)
tar_load(vct_merge)

vct_ref <- sapply(
    lst_yaml$ref,
    \(x) !all(simplify_is_null(x))
  )
len_raw <- length(vct_raw)
df_out <- summarize_major_main_steps(
  lst_yaml,
  vct_out.ref,
  vct_raw,
  vct_basic,
  vct_nw.sleep,
  vct_cal,
  vct_out.raw,
  vct_out.oak.pre,
  vct_out.cut,
  vct_ox_step,
  vct_ox_wlms,
  vct_ox_acti
)
lgl_all <- 
  df_out |> 
  rowwise() |> 
  mutate(
    all = all(c_across(
      !id
    ))
  ) |> 
  pull(all)
lst_summary <- summarize_metrics_main(lst_yaml,
                                      vct_ref,
                                      vct_merge)

```

# Input

Out of `r len_raw` raw files, `r sum(lgl_all)` successfully went through the pipeline.

# By Major Steps

Below is a table listing if each major step was successful for a file (TRUE) or unsuccessful (FALSE)

```{r}
#| label: tbl-major
#| echo: false

lst_green <- 
  list(
    if (vct_ref["do"]) {cells_body(columns = DO, rows = DO)},
    if (vct_ref["pal"]) {cells_body(columns = activPAL, rows = activPAL)},
    if (vct_ref["pass"]) {cells_body(columns = ActiPass, rows = ActiPass)},
    cells_body(columns = GGIR,          rows = GGIR),
    cells_body(columns = nw.sleep,      rows = nw.sleep),
    cells_body(columns = calibration,   rows = calibration),
    cells_body(columns = `raw methods`, rows = `raw methods`),
    cells_body(columns = oak.pre,       rows = oak.pre),
    cells_body(columns = cutpoints,     rows = cutpoints),
    cells_body(columns = stepcount,     rows = stepcount),
    cells_body(columns = walmsley,      rows = walmsley),
    cells_body(columns = actinet,       rows = actinet)
  ) |> 
  Filter(x = _,
         f = Negate(is.null))
lst_red <- 
  list(
    if (vct_ref["do"]) {cells_body(columns = DO, rows = !DO)},
    if (vct_ref["pal"]) {cells_body(columns = activPAL, rows = !activPAL)},
    if (vct_ref["pass"]) {cells_body(columns = ActiPass, rows = !ActiPass)},
    cells_body(columns = GGIR,          rows = !GGIR),
    cells_body(columns = nw.sleep,      rows = !nw.sleep),
    cells_body(columns = calibration,   rows = !calibration),
    cells_body(columns = `raw methods`, rows = !`raw methods`),
    cells_body(columns = oak.pre,       rows = !oak.pre),
    cells_body(columns = cutpoints,     rows = !cutpoints),
    cells_body(columns = stepcount,     rows = !stepcount),
    cells_body(columns = walmsley,      rows = !walmsley),
    cells_body(columns = actinet,       rows = !actinet)
  ) |> 
  Filter(x = _,
         f = Negate(is.null))
gt(df_out) |> 
  tab_style(
    style     = cell_fill(color = "#D9F1D5"),
    locations = lst_green
  ) |> 
  tab_style(
    style     = cell_fill(color = "#ea9999"),
    locations = lst_red
  )

```

# Totals by Configuration File

If all values are highlighted green, then the WAVES code is running successfully on your computer. If a column or row is highlighted in red, please share this .html file with the WAVES data team for follow up.

## MVPA (minutes)

```{r}
#| label: tbl-mvpa_total 
#| echo: false 
lst_summary$total_mvpa

```

## Sedentary (minutes)

```{r}
#| label: tbl-sed_total 
#| echo: false 
lst_summary$total_sed

```

## Steps

```{r}
#| label: tbl-step_total 
#| echo: false 
lst_summary$total_step

```

# tar_meta

```{r}
#| label: tar_meta
#| echo: false

tar_meta(targets_only = TRUE) |> 
  dplyr::filter(type != "branch") |> 
  select(name, warnings, error) |> 
  mutate(
    warnings = gsub(
      x = warnings,
      pattern = "\\w{0,1}package '.*' was built under R version 4.5.2.",
      replacement = ""
    )
  ) |> 
  kable()

```
